### 2020-01-11 defesa/tex/chapter/e3p.tex
wip

Among the approaches that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3PNT.
The other approach that showed good results was the numerical approximation one that uses Chebyshev interpolation. Ultimately this approach requires finding the eigenvalues of a companion matrix, this matrix, however, is usually going to be larger than the $6\times 6$, which is the size of the matrix needed to find the roots of the complex polynomial in \autoref{algoritmo:e3p}.

Details about getting the eigenvalues of a companion matrix, or determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity and can be found elsewhere in this work. Also, we assume that the $angle$ function used in the algorithm returns the angle of a complex number in the interval $[0, 2\pi)$.

@@

		\State $\hat{u}\gets (0,0)$
		\State $\hat{v} \gets v-u$
		\State $\hat{w} \gets w-u$

@@

In this section we show the results of an experiment made to study the numerical stability of \autoref{algoritmo:e3p}.
For every root found $\hat{\theta}$, we measure its error by $|\xi(\hat{\theta})$|.

>>>>

Among the methods that have been described here, converting $\xi$ into a complex polynomial was the chosen one as the basis of the algorithm for E3PNT.
The other approach that showed good results was the numerical approximation one that uses Chebyshev interpolation. Ultimately, this method requires finding the eigenvalues of a companion matrix, which is usually going to be larger than the $6\times 6$, which is the size of the companion matrix needed to find the roots of the complex polynomial in \autoref{algoritmo:e3p}.

Details about getting the eigenvalues of a companion matrix, and determining the center of a circumscribed circle of a triangle are omitted from \autoref{algoritmo:e3p} for the sake of clarity. 
Computing the coefficients of the complex polynomial $h$ is done in our implementation using a symbolic computation library for Python called Sympy (for more information about it see \citeonline{sympy}). This way, $c_0, \dots, c_{12}$ can be written as functions of E3PNT's instance.

@@

		\State $\hat{u}\gets (0,0)$ \Comment{Translate the system, so $u$ is at the origin.}
		\State $\hat{v} \gets v-u$
		\State $\hat{w} \gets w-u$

@@

In this section we show the results of an experiment we made to study the numerical stability of \autoref{algoritmo:e3p}.
For every root found $\hat{\theta}$, we measure its error by $|\xi(\hat{\theta})$|.
